Translating UML Class Diagrams and Sequence Diagrams to FO($\cdot$) to Facilitate Simulation and Verification

### 2018-06-05 IEEEtran/article.tex
superfluous -> redundant

\begin{itemize}
	\item \textbf{Many-to-many associations}: The presence of a many-to-many association is generally an indication that there is a class missing from the design.
	\item \textbf{Loose class}: If a class cannot be reached by navigating associations, that class is essentially useless and should be eliminated.
	\item \textbf{Superfluous associations}\cite{Balaban2015}: Consider figure \ref{fig:design-flaw}. In the association \textit{Alice}---\textit{Charlie}, the lower bounds for both roles are greater than the lower bounds in the association \textit{Bob}---\textit{David}. Similarly, the upper bounds for \textit{Alice}---\textit{Charlie} are less than the upper bounds for \textit{Bob}---\textit{David}. This means that the multiplicities for \textit{Bob}---\textit{David} are more permissive than those for \textit{Alice}---\textit{Charlie} and are thus unnecessary. Associations of this kind should be removed in order to improve the readability of the diagram.
\end{itemize}

\begin{figure}[!t]
	\centering
	\includegraphics[width=2.5in]{hierarchy}
	\caption{Example of loose class and superfluous association}
	\label{fig:design-flaw}
\end{figure}

@@

The rule that detects superfluous associations is too large to include in this article in a format that is reasonably understandable. It is structured as follows:

\begin{itemize}
	\item Classes \textit{x} and \textit{y} are associated. There is a class \textit{Sx} which is a superclass of \textit{x} and is associated with \textit{y}. Association \textit{x}---\textit{y} has a greater upper bound or a smaller lower bound at the \textit{x}-end, rendering \textit{Sx}---\textit{y} superfluous.
	\item Classes \textit{x} and \textit{y} are associated. There is a class \textit{Sy} which is a superclass of \textit{y} and is associated with \textit{x}. Association \textit{x}---\textit{y} has a greater upper bound or a smaller lower bound at the \textit{x}-end, rendering \textit{x}---\textit{Sy} superfluous.
	\item Classes \textit{x} and \textit{y} are associated. There are classes \textit{Sx}, a superclass of \textit{x}, and \textit{Sy}, a superclass of \textit{y}. Association \textit{x}---\textit{y} has a greater upper bound or a smaller lower bound at the \textit{x}-end, rendering \textit{Sx}---\textit{Sy} superfluous. 
\end{itemize}

We combine the information from the diagrams in figures \ref{fig:game-class} and \ref{fig:game-class} into one theory. IDP finds all many-to-many associations and concludes that \textit{Loose} is a loose class and that association \textit{Bob}---\textit{David} is superfluous.

>>>>

\begin{itemize}
	\item \textbf{Many-to-many associations}: The presence of a many-to-many association is generally an indication that there is a class missing from the design.
	\item \textbf{Loose class}: If a class cannot be reached by navigating associations, that class is essentially useless and should be eliminated.
	\item \textbf{Redundant associations}\cite{Balaban2015}: Consider figure \ref{fig:design-flaw}. In the association \textit{Alice}---\textit{Charlie}, the lower bounds for both roles are greater than the lower bounds in the association \textit{Bob}---\textit{David}. Similarly, the upper bounds for \textit{Alice}---\textit{Charlie} are less than the upper bounds for \textit{Bob}---\textit{David}. This means that the multiplicities for \textit{Bob}---\textit{David} are more permissive than those for \textit{Alice}---\textit{Charlie} and are thus unnecessary. Associations of this kind should be removed in order to improve the readability of the diagram.
\end{itemize}

\begin{figure}[!t]
	\centering
	\includegraphics[width=2.5in]{hierarchy}
	\caption{Example of loose class and redundant association}
	\label{fig:design-flaw}
\end{figure}

@@

The rule that detects redundant associations is too large to include in this article in a format that is reasonably understandable. It is structured as follows:

\begin{itemize}
	\item Classes \textit{x} and \textit{y} are associated. There is a class \textit{Sx} which is a superclass of \textit{x} and is associated with \textit{y}. Association \textit{x}---\textit{y} has a greater upper bound or a smaller lower bound at the \textit{x}-end, rendering \textit{Sx}---\textit{y} redundant.
	\item Classes \textit{x} and \textit{y} are associated. There is a class \textit{Sy} which is a superclass of \textit{y} and is associated with \textit{x}. Association \textit{x}---\textit{y} has a greater upper bound or a smaller lower bound at the \textit{x}-end, rendering \textit{x}---\textit{Sy} redundant.
	\item Classes \textit{x} and \textit{y} are associated. There are classes \textit{Sx}, a superclass of \textit{x}, and \textit{Sy}, a superclass of \textit{y}. Association \textit{x}---\textit{y} has a greater upper bound or a smaller lower bound at the \textit{x}-end, rendering \textit{Sx}---\textit{Sy} redundant. 
\end{itemize}

We combine the information from the diagrams in figures \ref{fig:game-class} and \ref{fig:game-class} into one theory. IDP finds all many-to-many associations and concludes that \textit{Loose} is a loose class and that association \textit{Bob}---\textit{David} is redundant.
